LHC abort gap monitor electronics upgrade

### 2024-03-11 paper.tex
added abstract and title of the paper

\title{preparation OF papers for \NoCaseChange{JACoW} conferences\thanks{Work supported by ...}}

\author{A. N. Author\thanks{email address}, H. Coauthor, Name of Institute or Affiliation, City, Country \\
		P. Contributor\textsuperscript{1}, Name of Institute or Affiliation, City, Country \\
		\textsuperscript{1}also at Name of Secondary Institute or Affiliation, City, Country}

@@

%
\begin{abstract}
   Many conference series have adopted the same standards
   for electronic publication and have joined the Joint
   Accelerator Conferences Website (JACoW) collaboration
   for the publication of their proceedings. This document
   describes the common requirements for the submission of
   papers to these conferences. Please consult individual
   conference information for page limits, method of electronic
   submission, etc. It is not intended that this should
   be a tutorial in word processing; the aim is to explain the
   particular requirements for electronic publication at
   www.JACoW.org. The abstract itself is to act as a stand-alone
   entity and, as such, should not include citations. Any acronyms 
   should be expanded on their first occurrence, both in the 
   abstract and in the rest of the paper. 
   The abstract itself is to act as a stand-alone entity and, 
   as such, should not include citations. Any acronyms should 
   be expanded on their first occurrence, both in the abstract 
   and in the rest of the paper.
\end{abstract}

>>>>

\title{LHC abort gap monitor electronics upgrade}

\author{P. Pacner\thanks{petr.pacner@cern.ch}, Brno University of Technology, Brno, Czech Republic \\
		S. B. Pedersen, D. Belohrad, M. M. Nieto, S. Mazzoni, CERN, Geneva, Switzerland}

@@

\begin{abstract}
    The LHC Abort Gap Monitor (AGM) is part of the LHC machine protection
    system (MPS) and is designed to measure the particle population in a 3us
    wide region known as the "abort gap." This region needs to be kept empty to
    ensure safe beam dumps. The AGM captures the synchrotron light generated in
    the visible part of the spectra and converts it into an electric signal.
    This signal is then processed by an acquisition system and can trigger the
    ‘abort gap cleaning’ process.\\
    The current AGM, which has been in operation since 2010, uses an analogue
    integrator ASIC and a 40 MHz analogue-to-digital (ADC) converter to provide
    the particle population information. However, this solution is now
    considered obsolete and is being replaced by a digital signal processing
    approach. Working directly in the digital domain not only offers more
    scalability but also better determinism and reliability. \\
    This work presents the new technical solution for the acquisition chain,
    compares the characteristics of both implementations, and showcases recent
    measurements conducted on the LHC ion and proton beams.
\end{abstract}
